Covariate and differential expression analysis of ROSMAP reprocessed counts Using Diagnosis as a covariate for TWAS

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Add In SynStore Steps

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798014';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- getRepo(repository = "kelshmo/Brain_Reg_Net", ref="branch", refName='CMC')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
#Set Used SynIDs For Provenance
Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
  "syn8691134", "syn3191087", "syn8698240"
)

@@

>>>>

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798014';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';

# Code WTF is this??
CODE <- Folder(name = "DLPFC - RSEM - EXPECTED COUNTS - GRCh37 - CQN - SVAandDiagnosisRegress - JKG", parentId = parentId)
CODE <- synStore(CODE)

#Set Used SynIDs For Provenance
Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
  "syn8691134", "syn3191087", "syn8698240"
)

@@

# Store enrichment results
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Corrected.tsv', 
                  name = 'SVA and Diagnosis Regressed Data', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'SVA_Diagnosis_Regressed'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
